Say Cheese! A Snapshot of Canadian Family Demographics

### 2022-03-21 outputs/paper/paper.Rmd
survey images

The supplementary survey can be found at https://forms.gle/jun4vZaAh247442s5 .

>>>>

The supplementary survey can be found at https://forms.gle/jun4vZaAh247442s5.

```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
knitr::include_graphics("D:/UofT/Y3 Winter/STA304/General-Social-Survey-on-Family-2017-/inputs/data")
```

![Survey Image 1](https://drive.google.com/uc?id=105Sr09qXQPzrvFUNmOd1qHG84V94jDEn)
![Survey Image 2](https://drive.google.com/uc?id=107y1yW9TqJINgvVqm0yfXLsdzld2BRtQ)
![Survey Image 3](https://drive.google.com/uc?id=107JteNN_kV37zsazeSRil85HA-Mur9YG)
![Survey Image 4](https://drive.google.com/uc?id=104sehzXe95lAC71JAclYGfhQ5Lpzh6sX)
![Survey Image 5](https://drive.google.com/uc?id=10ASJKQVaztg8YXOqzUTM1U1G4dCT0Z2B)
